---
title: "The report"
author: "XXX"
date: "`r Sys.Date()`"
output:
  pagedown::html_paged:
    toc: true
    css: ["default", "css/custom-page.css", "css/custom.css"]
    # change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: true
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
library(data.table)
knitr::opts_chunk$set(echo = TRUE)

```

# Part I

## Pagedown

Paginate the HTML Output of R Markdown with CSS for Print. You only need a modern web browser (e.g., Google Chrome) to generate PDF. No need to install LaTeX to get beautiful PDFs.

This R package stands on the shoulders of two giants to support typesetting with CSS for R Markdown documents: Paged.js and ReLaXed (we only borrowed some CSS from the ReLaXed repo and didn't really use the Node package).

You may install this package from Github:

## Page.js

Paged.js is an open-source library to display paginated content in the browser and to generate print books using web technology.
It contains a set of handlers for CSS transformations and fragmented layout which polyfill the Paged Media and Generated Content CSS modules, along with hooks to create new handlers for custom properties.
The currently supported properties can be found on the wiki.
A quick overview to getting started with Paged Media CSS and Paged.js is available on pagedmedia.org.

# Part II

## Pagedown

Paginate the HTML Output of R Markdown with CSS for Print. You only need a modern web browser (e.g., Google Chrome) to generate PDF. No need to install LaTeX to get beautiful PDFs.

This R package stands on the shoulders of two giants to support typesetting with CSS for R Markdown documents: Paged.js and ReLaXed (we only borrowed some CSS from the ReLaXed repo and didn't really use the Node package).

You may install this package from Github:

## Page.js

Paged.js is an open-source library to display paginated content in the browser and to generate print books using web technology.
It contains a set of handlers for CSS transformations and fragmented layout which polyfill the Paged Media and Generated Content CSS modules, along with hooks to create new handlers for custom properties.
The currently supported properties can be found on the wiki.
A quick overview to getting started with Paged Media CSS and Paged.js is available on pagedmedia.org.


```{js, include = FALSE}
// Repeat table headers
// from https://gitlab.pagedmedia.org/tools/pagedjs/issues/84
class RepeatingTableHeaders extends Paged.Handler {
  constructor(chunker, polisher, caller) {
    super(chunker, polisher, caller);
  }
  
  afterPageLayout(pageElement, page, breakToken, chunker) {
    // Find all split table elements
    let tables = pageElement.querySelectorAll("table[data-split-from]");
    
    tables.forEach((table) => {
      // Get the reference UUID of the node
      let ref = table.dataset.ref;
      // Find the node in the original source
      let sourceTable = chunker.source.querySelector("[data-ref='" + ref + "']");
      // Find if there is a header
      let header = sourceTable.querySelector("tbody");
      if (header) {
        // Clone the header element
        let clonedHeader = header.cloneNode(true);
        // Insert the header at the start of the split table
        table.insertBefore(clonedHeader, table.firstChild);
      }
    });
    
  }
}
Paged.registerHandlers(RepeatingTableHeaders);
```

```{r, echo = FALSE}
# dt <- fread('data/data.csv', encoding = 'UTF-8')
# dt <- dt[, head(.SD, 5), by = 'PORT_NAME', .SDcols = ]
# dt <- dt[, -c("CLASS_L1", "TYPE", "CR_HLD", "CR_M", "ER_M")]
# 
# dt[, `:=` (
#   AV = round(AV / 1e7, 2),
#   BUY_DATE = as.character(BUY_DATE),
#   UGL_RATIO = GCAMCPUB::f_fmt_pct(UGL_RATIO),
#   ER_HLD = GCAMCPUB::f_fmt_pct(ER_HLD),
#   CR_Y = GCAMCPUB::f_fmt_pct(CR_Y),
#   ER_Y = GCAMCPUB::f_fmt_pct(ER_Y)
# )]
# setnames(dt,
#   c("PORT_NAME", "SEC_CODE", "SEC_NAME", "AV", "BUY_DATE", "UGL_RATIO", "ER_HLD", "CR_Y", "ER_Y"),
#   c("账户名称", "证券代码", "证券名称", "账面价值（千万元）", "买入时间", "浮动盈亏/成本" ,
#     "持有期累计超额", "年初至今累计", "年初至今超额")
# )
# # knitr::kable(dt, "html")
gt::gt(Seatbelts)
```


