---
title: "The report"
author: "XXX"
date: "`r Sys.Date()`"
output:
  pagedown::html_paged:
    css: ["default", "css/custom-page.css", "css/custom.css", "css/custom-tbl.css"]
    self_contained: true
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
library(data.table)
knitr::opts_chunk$set(echo = TRUE)

```

# Part I

## Pagedown

Paginate the HTML Output of R Markdown with CSS for Print. You only need a modern web browser (e.g., Google Chrome) to generate PDF. No need to install LaTeX to get beautiful PDFs.

This R package stands on the shoulders of two giants to support typesetting with CSS for R Markdown documents: Paged.js and ReLaXed (we only borrowed some CSS from the ReLaXed repo and didn't really use the Node package).

You may install this package from Github:

## Page.js

Paged.js is an open-source library to display paginated content in the browser and to generate print books using web technology.
It contains a set of handlers for CSS transformations and fragmented layout which polyfill the Paged Media and Generated Content CSS modules, along with hooks to create new handlers for custom properties.
The currently supported properties can be found on the wiki.
A quick overview to getting started with Paged Media CSS and Paged.js is available on pagedmedia.org.

# Part II

## Pagedown

Paginate the HTML Output of R Markdown with CSS for Print. You only need a modern web browser (e.g., Google Chrome) to generate PDF. No need to install LaTeX to get beautiful PDFs.

This R package stands on the shoulders of two giants to support typesetting with CSS for R Markdown documents: Paged.js and ReLaXed (we only borrowed some CSS from the ReLaXed repo and didn't really use the Node package).

You may install this package from Github:

## Page.js

Paged.js is an open-source library to display paginated content in the browser and to generate print books using web technology.
It contains a set of handlers for CSS transformations and fragmented layout which polyfill the Paged Media and Generated Content CSS modules, along with hooks to create new handlers for custom properties.
The currently supported properties can be found on the wiki.
A quick overview to getting started with Paged Media CSS and Paged.js is available on pagedmedia.org.


```{js, include = FALSE}
// Repeat table headers
// from https://gitlab.pagedmedia.org/tools/pagedjs/issues/84
class RepeatingTableHeaders extends Paged.Handler {
  constructor(chunker, polisher, caller) {
    super(chunker, polisher, caller);
  }
  
  afterPageLayout(pageElement, page, breakToken, chunker) {
        // Find all split table elements
        let tables = pageElement.querySelectorAll("table[data-split-from]");

        tables.forEach((table) => {
            // There is an edge case where the previous page table 
            // has zero height (isn't visible).
            // To avoid double header we will only add header if there is none.
            let tableHeader = table.querySelector("thead");
            if (tableHeader) {
                return;
            }
            
            console.log(tableHeader)

            // Get the reference UUID of the node
            let ref = table.dataset.ref;
            // Find the node in the original source
            let sourceTable = chunker.source.querySelector("[data-ref='" + ref + "']");

            // Find if there is a header
            let sourceHeader = sourceTable.querySelector("thead");
            if (sourceHeader) {
                console.log("Table header was cloned, because it is splitted.");
                // Clone the header element
                let clonedHeader = sourceHeader.cloneNode(true);
                // Insert the header at the start of the split table
                table.insertBefore(clonedHeader, table.firstChild);
                
                console.log(table)
            }
        });

        // Find all tables
        tables = pageElement.querySelectorAll("table");

        // special case which might not fit for everyone
        tables.forEach((table) => {
            // if the table has no rows in body, hide it.
            // This happens because my render engine creates empty tables.
            let sourceBody = table.querySelector("tbody > tr");
            if (!sourceBody) {
                console.log("Table was hidden, because it has no rows in tbody.");
                table.style.visibility = "hidden";
                table.style.position = "absolute";

                var lineSpacer = table.nextSibling;
                if (lineSpacer) {
                    lineSpacer.style.visibility = "hidden";
                    lineSpacer.style.position = "absolute";
                }
            }
        });
    }

}

Paged.registerHandlers(RepeatingTableHeaders);
```

```{r, echo = FALSE}
library(gtExtras)
library(gt)
df <- as.data.frame(Seatbelts)
df |>
  gt() |>
  gt_theme_excel() |>
  tab_header(title = "Table styled like Excel")
```


```{r, echo = FALSE}
gt::gt(as.data.frame(Seatbelts))
```

YOU MUST HAVE TEXT AT BOTTOM OR IT WILL NOT PAGINATE TABLE

